%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Lulu}{Wang}{ \urlstyle{same}\url{http://lulu-wang.github.io} \\
\href{mailto:luluw1@berkeley.edu}{luluw1@berkeley.edu} | 510.735.5996
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UC Berkeley}
\descript{BS in Computer Science}
\location{Expected May 2019 | Berkeley, CA}
Art Practice Minor \\
\location{Major GPA: 3.3}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/lulu-wang}{\custombold{lulu-wang}} \\
LinkedIn://  \href{https://www.linkedin.com/in/luluwang25}{\custombold{luluwang25}} \\
YouTube://  \href{https://www.youtube.com/channel/UCdYrIU1HwvnvfsKthP5k95Q}{\custombold{aiishii}} \\
DevPost: // \href {https://devpost.com/lulu-wang?ref_content=user-portfolio&ref_feature=portfolio&ref_medium=global-nav}{\custombold{Lulu Wang}}\\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Functional Programming \\
Data Abstraction \\
Data Structures \\
Algorithms \\
Object Oriented Programming \\
Linear Algebra \\
Unix Tools and Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Java \textbullet{}   Python \textbullet{} Scheme \textbullet{} SQL \\
HTML \textbullet{} CSS \textbullet{} Javascript \textbullet{} C\# \\ 
\sectionsep
\subsection{Tools}
Adobe Creative Suite \textbullet{} XCode \\
IntelliJ \textbullet{} Unity \textbullet{} Sketch
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{UC Berkeley}
\descript{| CS61A Academic Intern }
\location{ May 2017 – Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Provide tutoring assistance for students during office hours and labs;
\item Aided course staff in organizing weekly teaching schedules.
\end{tightemize}
\sectionsep

\runsubsection{MyBeeble}
\descript{| UX/UI Intern }
\location{June 2016 – Jan 2017 | Berkeley, CA}
\begin{tightemize}
\item Headed the redesign of the app’s user interface, including layout and color scheme
changes; \item Created workflow diagrams and oversaw navigation reconstruction; \item Conducted industry and competition research to optimize user experience. \end{tightemize}
\sectionsep

\runsubsection{Red Iron Labs}
\descript{| Junior Game Assistant}
\location{June 2013 – June 2013 | Calgary, AB}
\begin{tightemize}
\item Designed and implemented \textbf{\href{http://redironlabs.ca}{company website}} using Wordpress;
\item Conducted early crowdfunding research for the company's first virtual reality multi-console game, Abduction;\item Assisted in alpha testing of the game.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership}
\runsubsection{Hackers @ Berkeley}
\descript{| Officer}
\location{Sept 2016 – Present | Berkeley, CA}
\begin{tightemize}
\item Designed promotional banners for student workshops on OpenCV and iOS development.\item Coordinated with various companies to provide organization funding.
\end{tightemize}
\sectionsep

\runsubsection{Berkeley Builds Designathon}
\descript{| Director}
\location{April 2017 | Berkeley, CA}
\begin{tightemize}
\item Brought together student organizations and nonprofit organizations to create technical solutions to real-world problems. Designed event logo, banners, and T-shirt.
\item Helped raise \$1000 for the event through collaborating with student organizations.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Robot Flame War}
\location{TreeHacks}
An AI-based chatroom using Flask and Django. Personally responsible for researching and implementing web app using Socket.io.
\sectionsep

\runsubsection{Mochi Hop}
\location{}
A web-based game built with Phaser framework and Javascript. Created sprites and game graphics, programmed in under a week.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2015	     & National & Rotary International Get to Know Art Contest Winner\\
2016	     & National & Euclid Mathematics Contest Top 25\%\\
\end{tabular}
\sectionsep


\end{minipage} 
\end{document}
